PropOcData2

### 2021-07-18 R/PropOc Data 3D.Rmd
added quality control for raw data import

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
# Importing whole data sets to identify distribution of data
```{r read whole data sets}
ReadPropOc<-function(sampleName){
propOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", sampleName,".csv"),header = T)
data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}

@@

rawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01Laptop",".csv"),header = T)

#QC for data:
countData<-rawPropOcData %>% group_by(source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))
CheckPropOc<-rawPropOcData %>% filter(PropOc>1.05|PropOc<0)
ggplot()+
  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
  #labs(title ="title")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

>>>>

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
# Importing whole data sets to identify distribution of data
```{r read whole data sets}

ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

propOcDatafolder<-'/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data'
propOcDatafileList<-list.files(path = propOcDatafolder, full.names = TRUE)
rawPropOcDataList<-map(propOcDatafileList,ReadPropOcFile)
rawPropOcData<-bind_rows(rawPropOcDataList)
rawPropOcData<-rawPropOcData %>% filter(!SampleCode=="mono_d1_01Slim") %>%  filter(!SampleCode=="mono_d1_02Slim")

#QC for data:
##How much data is just straight up missing?
#####
countData<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))

countData2<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
##How much of the missing data matters?

#first, remove the unnecessary conditions
removablePropOc <- bind_rows(rawPropOcData %>% filter(Condition == "mono") %>% filter(!source == "finalRR"), #Pa in Sa mono culture
                       rawPropOcData %>% filter(Condition == "papqsL") %>% filter(!source == "finalGG"),#Sa in all Pa mono cultures
                       rawPropOcData %>% filter(Condition == "pawt") %>% filter(!source == "finalGG"),
                       rawPropOcData %>% filter(Condition == "paphz") %>% filter(!source == "finalGG"))
rawPropOcDataClean <- anti_join(rawPropOcData, removablePropOc)

##then, bad samples
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "mono_d1_03")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_14")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_02")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_04")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_10")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "wt_d4_07")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "papqsL_d4_02")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pawt_d4_05")
rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_06")

#Do it again
countDataClean<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))

countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
#it got a little better, but not that much...
#####
#How much of it is outside the ideal boundaries?

CheckBenchmark<-function(benchmark){
CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1)

ggplot()+
  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
  #labs(title ="title")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

GetHistograms<-function(sample){

data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}

@@

testrawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01",".csv"),header = T)
